Big Data with High Performance Computing (HPC)

### 2016-01-14 Tex_Files/paper.tex
Adam memory optimization added/completed
Adam memory optimization added/completed.
Adam Global Parameter Server section started/incomplete.

\subsection{Intra machine architecture and optimizations}

@@

Earlier we mentioned that neural networks are resilient so that we could use asynchronous communication between machines and global Parameter Server for updating weights. Same argument could be applied here for weight updates by threads on a single machine. On each machine a shared model holds the weights from all of threads weight updates. In order to avoid the lock times, threads update weights on the shared model without locking. Resilience of the neural networks along with commutativity and associativity properties of weight updates make the model work despite possible overwriting and race conditions of weight updates. This is one of the most important optimizations that allow scaling of deep neural network training process.

>>>>

\subsection*{Intra machine architecture and optimizations}

@@

Earlier we mentioned that neural networks are resilient so that we could use asynchronous communication between machines and global Parameter Server for updating weights. Same argument could be applied here for weight updates by threads on a single machine. On each machine a shared model holds the weights from all of threads weight updates. In order to avoid the lock times, threads update weights on the shared model without locking. Resilience of the neural networks along with commutativity and associativity properties of weight updates make the model work despite possible overwriting and race conditions of weight updates. This is one of the most important optimizations that allow scaling of deep neural network training process.\\

\subsection*{Memory optimizations}

During the training process weights need to be transmitted back and forth among layers. In order to minimize redundant copies, a pointer is passed along rather than rather than the values. In addition, in the model parallelism architectures, there are some communication between layers across multiple machines. These non-local communications are performed through a library built by project Adam team. The library is custom fit to the communication design of Adam, which supports pointer addressing to blocks of neurons that their output needs communication.\\

The partitioning of the models is Adam is done in a way that the working sets fit inside a L3 cache. Besides, an assembly kernel is implemented and tuned to exploit the locality during feed-forward and back propagation. The kernel allows for optimal matrix multiplication whether row major or column major blocks of weights are to be multiplied.\\

\subsection*{Global Parameter Server}

The Global Parameter Server holds the updated weights of the overall model from all machines. Due to high volume of weight updates, the Global Parameter Server of Adam require a more complex design rather than a conventional key value store. Figure \ref{fig:adam_global_param} depicts the architecture of the Global Server node for Adam.
\begin{figure}[h]
	\includegraphics[scale=0.42]{./images/adam_global_param_server.png}
	\centering
	\caption{Global Parameter Server architecture of Adam\cite{chilimbi2014project}.}
	\label{fig:adam_global_param}
\end{figure}
